\documentclass{article}
\usepackage{csquotes}
\usepackage{enumitem}
\def\SLOname{Euler's Collective }
\def\title{\textbf{NUGSS SLO CONSTITUTION}\\ \textbf{\SLOname}\\\textbf{CONSTITUION}\\\today}
\begin{document}
{
	\large
	\begin{center}
\title
\end{center}
}

\section{SLO NAME}
\subsection{}
The official name of the SLO will be \enquote{UNBC \SLOname}.

\subsection{}
No other name shall be used in the advertisement and the representation of the SLO.

\section{Purpose}
\subsection{}
To facilitate and host discussion on and relating to mathematical topics.
\subsection{}
Organize mathematical competitions to facilitate growth through competition.
\subsection{}
Promote enthusiasm in mathematics in the student body.
\section{MISSION STATEMENT}
\subsection{}
The Mission Statement of \SLOname  is:
To strengthen the mathematical community at UNBC.
\section{MEMBERSHIP}
\subsection{}
Membership is open to everyone.

\subsection{}
Only undergraduate of UNBC are eligible to hold voting privileges and executive positions in the organization.
\subsection{}
Associate non-voting members should be allowed.
\section{MEETING}
\subsection{}
The Chair of all the meetings will be chosen by the members of the SLO.
\subsection{}
The Chair will be another member of the SLO aside from the executive.
\subsection{}
At least three (3) general meetings shall be held during academic year, including the SLO's Annual General Meeting.
\subsection{}
members must be informed of the Annual General Meeting at least seven (7) days in advance.
\subsection{}
Quorum shall consist of fifty percent (50\%) plus one voting member.
\subsection{}
Executive decisions shall not be autocratic. If there is any opposition to an executive decision, the decision must be taken to a vote of the membership.
\section{EXECUTIVE BOARD AND THEIR DUTIES}
\subsection{}
The Executive Board shall consist of:
\begin{enumerate}[label=\alph*)]
	\item President: 
		\begin{itemize}
			\item oversees the other members of the Executive Board in their duties; and,
			\item has signing authority for the SLO
		\end{itemize}
	\item Vice-President:
		\begin{itemize}
			\item assists the President in his/her duties; and,
			\item assumes all power of the President in his/her absence.
		\end{itemize}
	\item Treasurer:
		\begin{itemize}
			\item is responsible for all financial dealings of the SLO;
			\item keeps complete record of all financial transactions
		\end{itemize}
	\item Social Media Manager:
		\begin{itemize}
			\item is responsible for managing the social media;
			\item is responsible for promotion of the SLO and events concerning the SLO
		\end{itemize}
	\item Secretary:
		\begin{itemize}
			\item is responsible for minute taking at the SLO's meetings
			\item makes sure minutes are passed by the Board,
			\item and keeps the complete record of all the SLO members.
		\end{itemize}
\end{enumerate}
\section{FINANCES}
\subsection{}
the executive will set a membership fee annually.
\subsection{}
The finances of the organization must be handled exclusively by the organization and kept separate from any other group.
\subsection{}
Any surplus resulting from the yearly operations of the group should be transferred to reserve for future use and no part of the surplus will be payable to any member.
\subsection{}
SLO must provide the Board of Directors or General Manager with their up to date bank account statements, cancelled cheques, financial ledger, deposit books and any other financial document that is deemed necessary to assure that accurate accounts are being properly kept.
\subsection{}
In the event of the dissolution of the group, all surplus and assets will be transferred to NUGSS to be placed in NUGSS's alloted funds for SLOs.
\section{ELECTIONS}
\subsection{}
The Executive Committee of the SLO must be elected from and by the membership by a majority vote.
\subsection{}
The election shall be held by secret ballot.
\section{AMENDMENTS}
\subsection{}
Amendments to the constitution shall be made at the Annual General Meeting.
\subsection{}
Amendments to the constitution must pass by a tow-thirds (2/3) majority vote of the members present.
\section{IMPEACHMENT}
\subsection{}
A motion to remove a member of the SLO must be signed by at least five percent (5\%) of the regular members of the SLO.
\subsection{}
The motion shall be presented in writing at a regular meeting of the SLO where it shall be inscribed on the agenda of the next regular meeting of the SLO, whereupon the impeached person will be give right to defend his/her actions.
\subsection{}
A quorum of one-half (1/2) of the voting members of the SLO is required to consider a motion to remove a member of the SLO.
\subsection{}
A two-thirds (2/3) majority vote of all member's present shall be required to remove a member of the SLO and any responsibilities or privileges associated with such.
\section{AGENCY}
\subsection{}
The SLO is not an agent of NUGSS and the SLO's views and actions do not represent those of NUGSS.
\end{document}
